\tit

### 2021-02-17 paper.tex
shorten subsection title

\subsectionl{Transporting Algebraic Properties}

@@

Fortunately, there is a simple way to encapsulate indexed types into simple (non-indexed) types, namely existential quantification.
For instance, {\AF{∃} \AD{Dec}} and {\AF{∃} \AD{(\ARe{Lang} \APo ∞)}} are simple types.
For a type family {\AB f \AK : \AB A \AK → \APT Set⇃}, values of type {\AF ∃ \AB f} are pairs {(\AB a , \AB b)} with {\AB a \AK : \AB A} and {\AB b \AK : \AB f \AB a}.
We can also encapsulate dependently typed \emph{operations} on indexed types into simply typed operations on the (simply typed) existentially wrapped versions of those types.
For instance, consider language union from \figref{symbolic-api}:
\begin{code}
% Copied from latex/Symbolic.tex
\>[2]\AgdaOperator{\AgdaInductiveConstructor{\AgdaUnderscore{}∪\AgdaUnderscore{}}}%
\>[7]\AgdaSymbol{:}\AgdaSpace{}%
\AgdaDatatype{Lang}%
\>[15]\AgdaGeneralizable{P}%
\>[18]\AgdaSymbol{→}\AgdaSpace{}%
\AgdaDatatype{Lang}\AgdaSpace{}%
\AgdaGeneralizable{Q}%
\>[28]\AgdaSymbol{→}\AgdaSpace{}%
\AgdaDatatype{Lang}\AgdaSpace{}%
\AgdaSymbol{(}\AgdaGeneralizable{P}%
\>[39]\AgdaOperator{\AgdaFunction{◬.∪}}%
\>[44]\AgdaGeneralizable{Q}\AgdaSymbol{)}\<%
\end{code}
Referring to the type and operations of \figref{symbolic-api} via the module prefix ``{◬.}\hspace{0.05em}'', define \agda{wrapped-Lang}
Then wrap union as follows:
\agda{wrapped-union}
Note that the type-level language components of the arguments and result are left to be inferred by the compiler.
\rnc\source{Existential}
Indexed operations of all arities for a type family \AB{f} can be systematically wrapped in this style, as shown in
\figrefdef{inj}{Existential wrappers}{\agda{inj}}, this time with the inferable components filled in for clarity.
Then wrapped union can be defined simply as {\AF{\_∪\_} \AS = \AF{inj₂} \AIC{◬.\_∪\_}} and likewise for the other operations.

>>>>

\subsectionl{Transporting Properties}

@@

Fortunately, there is a simple way to encapsulate indexed types into simple (non-indexed) types, namely existential quantification.
For instance, {\AF{∃} \AD{Dec}} and {\AF{∃} \AD{(\ARe{Lang} \APo ∞)}} are simple types.
For a type family {\AB F \AK : \AB A \AK → \APT Set⇃}, values of type {\AF ∃ \AB F} are pairs {(\AB a , \AB b)} with {\AB a \AK : \AB A} and {\AB b \AK : \AB F \AB a}.
We can also encapsulate dependently typed \emph{operations} on indexed types into simply typed operations on the (simply typed) existentially wrapped versions of those types.
For instance, consider language union from \figref{symbolic-api}:
\begin{code}
% Copied from latex/Symbolic.tex
\>[2]\AgdaOperator{\AgdaInductiveConstructor{\AgdaUnderscore{}∪\AgdaUnderscore{}}}%
\>[7]\AgdaSymbol{:}\AgdaSpace{}%
\AgdaDatatype{Lang}%
\>[15]\AgdaGeneralizable{P}%
\>[18]\AgdaSymbol{→}\AgdaSpace{}%
\AgdaDatatype{Lang}\AgdaSpace{}%
\AgdaGeneralizable{Q}%
\>[28]\AgdaSymbol{→}\AgdaSpace{}%
\AgdaDatatype{Lang}\AgdaSpace{}%
\AgdaSymbol{(}\AgdaGeneralizable{P}%
\>[39]\AgdaOperator{\AgdaFunction{◬.∪}}%
\>[44]\AgdaGeneralizable{Q}\AgdaSymbol{)}\<%
\end{code}
Referring to the type and operations of \figref{symbolic-api} via the module prefix ``{◬.}\hspace{0.05em}'', define \agda{wrapped-Lang}
Then wrap union as follows:
\agda{wrapped-union}
Note that the type-level language components of the arguments and result are left to be inferred by the compiler.
\rnc\source{Existential}
Indexed operations of all arities for a type family \AB{F} can be systematically wrapped in this style, as shown in
\figrefdef{inj}{Existential wrappers}{\agda{inj}}, this time with the inferable components filled in for clarity.
Then wrapped union can be defined simply as {\AF{\_∪\_} \AS = \AF{inj₂} \AIC{◬.\_∪\_}} and likewise for the other operations.
